### 2025-02-20 introduction.tex
e

Quantitative risk management is a key component of modern financial systems.
Successful risk management practice can ensure the stability and resilience against a variety of risks.
For financial products such as option portfolios and variable annuity (VA) contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
VA contracts are a popular type of complex insurance product that is linked to the performance of underlying assets.
It provides a guaranteed minimum income benefit to the policyholder regardless of the performance of the underlying assets.

@@

The number of inner simulations required to achieve a desired level of accuracy for each outer scenario can be intractably large.

@@

The risk management of VAs is a challenging problem due to the complex interactions between the policyholder's behavior, the financial market dynamics, and the insurer's risk management strategies.

@@

Monte Carlo simulations are widely used for modeling and analyzing complex systems that are probabilistic in nature. 
These simulations often require a substantial amount of computational resources, especially when a high degree of accuracy or a high number of iterations is necessary~\citep{glasserman2004monte}. 
Metamodeling addresses this challenge by constructing an approximate model (known as ametamodel) that emulates the behavior of the original simulation model with much less computational effort.
The metamodel serves as a predictive model that maps input variables to output responses. 
Learning from a set of simulation runs, the metamodel can generalize and predict outputs for new inputs without running the full simulation.
Metamodeling is particularly useful when the simulation model is computationally expensive. 
By replacing the simulation model with a metamodel, the computational cost of evaluating the model can be substantially reduced. 
This allows for faster convergence of simulation-based estimators.

>>>>

Risk management is a key component of modern financial systems.
Successful risk management practice can enhance financial stability and resilience for individual companies and for the financial system too.
Variable annuity (VA) contracts are a popular type of complex insurance product that is linked to the performance of underlying assets.
They provide a guaranteed minimum income benefit to the policyholder regardless of the performance of the underlying assets.

@@

The number of inner simulations required to achieve a desired level of accuracy for each outer scenario can be large.

@@

Risk management of VAs is a challenging problem due to the complex interactions between the policyholder's behavior and the financial market dynamics.

@@

Monte Carlo simulations are widely used for modeling and analyzing complex systems that are probabilistic in nature. 
These simulations often require a substantial amount of computational resources, especially when a high degree of accuracy or a high number of iterations is necessary~\citep{glasserman2004monte}. 
Metamodeling addresses this challenge by constructing an approximate model (known as a metamodel) that emulates the behavior of the original simulation model with much less computational effort.
The metamodel serves as a predictive model that maps input variables to output responses. 
Learning from a set of simulation runs, the metamodel can generalize and predict outputs for new inputs without running the full simulation.
Metamodeling is particularly useful when the simulation model is computationally expensive. 
By replacing the simulation model with a metamodel, the computational cost of evaluating the model can be substantially reduced. 
This allows for faster convergence of simulation-based estimators.

### 2025-02-20 uw-ethesis-frontpgs.tex
e

Additionally, I extend my sincere thanks to my best friends, who have stood by me during the most challenging times. 
Their unwavering support and encouragement have been a constant source of strength that helped me overcome obstacles and maintained my motivation throughout this process. 
Words cannot fully convey how much their presence has meant to me over these years.

>>>>

Additionally, I extend my sincere thanks to my best friends, who have stood by me during the most challenging times. 
Their unwavering support and encouragement have been a constant source of strength that has helped me overcome obstacles and maintain my motivation throughout this process. 
Words cannot fully convey how much their presence has meant to me over these years.
